Association between SARS-CoV-2 and metagenomic content of samples from the Huanan Seafood Market

### 2023-06-29 paper/paper.tex
Reviewer 1 point 2: discuss epi of market more

But by mid to late January of 2020, it was clear SARS-CoV-2 was spreading from human to human, and had been for some time~\citep{chan2020familial,phan2020importation,li2020early,nishiura2020initial}.
In addition, Chinese scientists published papers reporting that some of the earliest identified human cases in December 2019 had no link to the Huanan Seafood Market~\citep{huang2020clinical,chen2020epidemiological}.
Thus began a debate that continues to this day: was the market an initial source of zoonotic infections from animals, or was it simply a superspreading site that amplified earlier human infections from another source~\citep{cohen2020wuhan}?

It is universally agreed that there were human cases of SARS-CoV-2 at the Huanan Seafood Market by mid December of 2019~\citep{li2020early}.
It is also known that some animals susceptible to SARS-CoV-2 were sold at the market~\citep{xiao2021animal}.
The unanswered question is if any animals were infected, and if so whether they infected humans or were infected by them.

>>>>

But by mid to late January of 2020, it was clear SARS-CoV-2 was spreading from human to human, and had been for some time~\citep{chan2020familial,phan2020importation,li2020early,nishiura2020initial}.
In addition, Chinese scientists published papers reporting that some of the earliest identified human cases in December 2019 had no link to the Huanan Seafood Market~\citep{huang2020clinical,chen2020epidemiological,zhang2020viral}.
Thus began a debate that continues to this day: was the market an initial source of zoonotic infections from animals, or was it simply a superspreading site that amplified earlier human infections from another source~\citep{cohen2020wuhan}?

Some papers have argued that the fact that many of the known human cases from December 2019 are centered around market indicates it was the original source of the virus~\citep{worobey2022huanan}, and that an early two-mutation polytomy in the SARS-CoV-2 phylogenetic tree suggests multiple zoonotic jumps there~\citep{pekar2022molecular}.
Other papers have argued that reports of earlier cases unlinked to the market~\citep{huang2020clinical,chen2020epidemiological,zhang2020viral,ma2020SCMP} and uncertainties about the completeness of case data provided by the Chinese government~\citep{cohen2022anywhere,hvistendahl2023} mean that the first human infections could have occurred upstream of the December 2019 cases at the market~\citep{pekar2021timing,pipes2021assessing,bloom2021recovery}.

Despite these disputes, it is universally agreed that there were human cases of SARS-CoV-2 at the Huanan Seafood Market by mid December of 2019~\citep{li2020early}, and that some animals susceptible to SARS-CoV-2 were sold at the market~\citep{xiao2021animal}.
The key unanswered question is if any animals were infected, and if so whether they infected humans or were infected by them.
